%کلمات کلیدی انگلیسی
\latinkeywords{
  transportation, traffic speed prediction, deep neural networks
}
%چکیده انگلیسی

\en-abstract{
  Predicting traffic speed is essential to control and direct it. Due to the complexity and nonlinearity of traffic speed methods
The ancients could not predict traffic well for long and medium time travel. Accurate and immediate forecasting
Traffic speed is an important issue for individuals and organizations providing transportation services and even the government because transportation
Transportation plays an important role in every person's life and is one of the main capabilities in the intelligent transportation system.
Goes. In this project, we try to predict the traffic speed in some by using deep neural networks.
Pay attention to specific points (such as intersections and squares). Using the vast amount of data available today as well
Hardware Advancement We can train deep networks that were not teachable in the past and their high capability
Use in predicting complex issues. In this report, a torsional-spatial graph network is used to predict speed
We used traffic and using the evaluation results of this model on two real data sets, we showed that this network
Deep can effectively understand comprehensive spatio-temporal correlations and thus perform well.
}

%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}
